Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-19 cav2017/cav2017.tex
make fig 1 and fig 2 look alike
subsections don't have all the words in the title capitalized

%-------------------------------
\subsection{Related Work}
\label{sec:relw}
%-------------------------------

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Numeric Representations and Soundness} 
\label{sec:numeric_rep}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Fixed Word Length Effects on Matrix Multiplications}
\label{sec:cof_fwl}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller and the observer
exist in a digital program, hence their domain is $\mathbb{R}\langle I,F,E\rangle$. This has two separate effects
on the model. If we recall equation \eqref{eq:to_of}, the matrices of the observer and the controller  are not necessarily those of the plant.
In fact we have $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{C}_o, \mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F,E\rangle^*$
Where $*$ represents the appropriate dimension for each matrix.
Unfortunately this means that although combined matrices such as $\mat{A}_t$ are in the reals, they suffer from
the fixed word restrictions in their composing matrices.
The second effect corresponds to the rounding errors in the calculation of $\hat{x}_{k+1}, u_k$. These will introduce a new source of quantiztion noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
The estimation of $\hat{\vec{x}}$ corresponds to the sum of three matrix-vector multiplications (we assume $\mat{C}_o$ in Objective form). Each of these has a coefficient-wise error bound $c_{min(max(e_{j1}+e_{j2}))}$. Hence the overall $\overline{\delta}_{\hat{x}}=3nc_{min(max(e_{j1}+e_{j2}))}$. The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=nc_{min(max(e_{k1}+e_{k2}))}+\sum_{k=1}^nc_k\overline{\delta}_{\hat{x}})=3n|\mat{K}|_1c_{min(max(e_{j1}+e_{j2}))}+nc_{min(max(e_{k1}+e_{k2}))}$

%-------------------------------
\subsection{Safety specifications for Cyber-Physical Systems}
\label{ssec:safety}
%-------------------------------

@@

We investigate two different approaches of integrating solution generalisation 
into CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which 
enables abstraction refinement inside the CEGIS loop. 
\item[2.] The second approach relies on computing a completeness threshold $k$ for each loop such that it is sufficient to 
unroll the corresponding loop $k$ times. For this approach the generalisation step is given as an incremental
increase of precision and sampling rate.
\end{itemize}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General Architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesizer is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with Abstraction Refinement}
\label{sec:CEGIS-abstraction-refinement}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsubsection{Verification of a Controllable Observed System}
\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

@@

   \&\node[fill=yellow!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=yellow!20,align=center] (abstract) {\sc 4. abstraction};

@@

   \& \node[fill=yellow!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesiser};

@@

   \& \node[fill=yellow!20,align=center, minimum width=4cm] (verify) {\sc 3. verifier ($\Psi$)};

@@

   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with Precision and Sampling Rate Incrementation}
\label{sec:CEGIS-precision-incrementation}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%-------------------------------
\subsection{Description of the Benchmarks}
%-------------------------------

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Discretising Continuous Space Dynamics}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Modelling Quantization as noise}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Controllable Canonical Form} \label{sec:reachable}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Observable Canonical Form} \label{sec:observable}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The Controllable Canonical Form is ideal when we have access to the state space. However, in most cyberphisical
systems, only the outputs of the plant can be observed, hence we require an Observable Canonical Form.
For SISO systems, this is:
\begin{align}
\label{of_SISO}
\mat{A}_{of}=&\left[
\begin{array}{ccccc}
0&0&0&\cdots&-a_n\\
1&0&0&\cdots&-a_{n-1}\\
0&1&0&\cdots&-a_{n-2}\\
\vdots&\ddots&\ddots&\ddots&\vdots\\
0&0&\cdots&1&-a_1
\end{array}\right],
\mat{B}_{of}=\left[
\begin{array}{c}
\eta_n\\ \eta_{n-1}\\ \vdots\\ \eta_1
\end{array}\right]\\
\mat{C}_{of}=&[\begin{array}{ccccc}0&0&\cdots&0&1\end{array}] \nonumber
\end{align}

>>>>

%-------------------------------
\subsection{Related work}
\label{sec:relw}
%-------------------------------

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Numeric representations and soundness} 
\label{sec:numeric_rep}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Fixed word length effects on matrix multiplications}
\label{sec:cof_fwl}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller and the observer
exist in a digital program, hence their domain is $\mathbb{R}\langle I,F,E\rangle$. This has two separate effects
on the model. If we recall equation \eqref{eq:to_of}, the matrices of the observer and the controller  are not necessarily those of the plant.
In fact we have $\mat{A},\mat{B},\mat{C} \in \mathbb{R}^*$, $\mat{A}_o,\mat{B}_o,\mat{C}_o, \mat{K}_d, \mat{L}_d \in \mathbb{R}\langle I,F,E\rangle^*$
Where $*$ represents the appropriate dimension for each matrix.
Unfortunately this means that although combined matrices such as $\mat{A}_t$ are in the reals, they suffer from
the fixed word restrictions in their composing matrices.
The second effect corresponds to the rounding errors in the calculation of $\hat{x}_{k+1}, u_k$. These will introduce a new source of quantiztion noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
The estimation of $\hat{\vec{x}}$ corresponds to the sum of three matrix-vector multiplications (we assume $\mat{C}_o$ in Objective form). Each of these has a coefficient-wise error bound $c_{min(max(e_{j1}+e_{j2}))}$. Hence the overall $\overline{\delta}_{\hat{x}}=3nc_{min(max(e_{j1}+e_{j2}))}$. The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=nc_{min(max(e_{k1}+e_{k2}))}+\sum_{k=1}^nc_k\overline{\delta}_{\hat{x}})=3n|\mat{K}|_1c_{min(max(e_{j1}+e_{j2}))}+nc_{min(max(e_{k1}+e_{k2}))}$

%-------------------------------
\subsection{Safety specifications for cyber-physical systems}
\label{ssec:safety}
%-------------------------------

@@

We investigate two different approaches of integrating solution generalisation 
into CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which 
enables abstraction refinement inside the CEGIS loop. 
\item[2.] The second approach relies on computing a completeness threshold $k$ for each loop such that it is sufficient to 
unroll the corresponding loop $k$ times. For this approach the generalisation step is given as an incremental
increase of precision and sampling rate.
\end{itemize}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesizer is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with abstraction refinement}
\label{sec:CEGIS-abstraction-refinement}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsubsection{Verification of a controllable observed system}
\label{sec:cof_verification}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

{\scriptsize

@@

   \&\node[fill=gray!20,align=center] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstraction};

@@

   \& \node[fill=gray!20,align=center, minimum width=3cm] (synth) {\sc 2. synthesise};

@@

   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\Psi$)};

@@

   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{CEGIS with precision and sampling rate incrementation}
\label{sec:CEGIS-precision-incrementation}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%-------------------------------
\subsection{Description of the benchmarks}
%-------------------------------

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Discretising continuous space dynamics}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Modelling quantization as noise}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Controllable canonical form} \label{sec:reachable}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Observable canonical form} \label{sec:observable}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The Controllable Canonical Form is ideal when we have access to the state space. However, in most cyberphisical
systems, only the outputs of the plant can be observed, hence we require an Observable Canonical Form.
For SISO systems, this is:
\begin{align}
\label{of_SISO}
\mat{A}_{of}=&\left[
\begin{array}{ccccc}
0&0&0&\cdots&-a_n\\
1&0&0&\cdots&-a_{n-1}\\
0&1&0&\cdots&-a_{n-2}\\
\vdots&\ddots&\ddots&\ddots&\vdots\\
0&0&\cdots&1&-a_1
\end{array}\right],
\mat{B}_{of}=\left[
\begin{array}{c}
\eta_n\\ \eta_{n-1}\\ \vdots\\ \eta_1
\end{array}\right]\\
\mat{C}_{of}=&[\begin{array}{ccccc}0&0&\cdots&0&1\end{array}] \nonumber
\end{align}
